Learning Actionable Analytics (with applications for reducing defects and reducing runtimes)

### 2015-05-15 how.tex
Updates from ShareLaTeX

One way to assess the validity of our predictions is to consider the space that generates
them. \fig{howxy} is from the {\em ivy} data
set. It shows (1)~the training cases and (2)~the test cases and (3)~the
test cases displaced after applying HOW's plans.
To generate that figure, we placed all of 1+2+3 into the same data set then computed the first
two  components (using PCA). Note that the  the   displaced test
cases  (shown in green)  fall closer to the training cases (shown in gray) than
the test cases (shown in red).  That is, if we believe
that the gray data is  suitable for assessing
the test cases (as indicated by the {\em ivy} results from \fig{j}), then it follows
that we believe even more in the predictions
generated from the displaced data).

This pattern of \fig{howxy} (where the displaced test cases are found in the same
region as the training data) has been observed in all the other data sets studied in this
paper. Hence, the
predictors learned from these training data have some authority in the regions
used to generate our predictions regarding the effects of planning\footnote{If the reader is concerned that this 2d projection
losses important information, then they should note that two separate  studies~\cite{papa13,divya15}
have confirmed that building defect predictors from this 2d space are just as effective
as predictors learned using all the defect attributes of \fig{ck}.}.

>>>>

%XXX begin rahul 
One way to assess the validity of our predictions is to consider the space that generates
them. \fig{howxy} is from the {\em ivy} data
set. It shows (1)~the training cases and (2)~the test cases and (3)~the
test cases displaced after applying HOW's plans.
To generate that figure, we placed all of 1+2+3 into the same data set then computed the first
two  components (using PCA). Note that the  the   displaced test
cases  (shown in green)  fall closer to the training cases (shown in gray) than
the test cases (shown in red).  That is, if we believe
that the gray data is  suitable for assessing
the test cases (as indicated by the {\em ivy} results from \fig{j}), then it follows
that we believe even more in the predictions
generated from the displaced data).

This pattern of \fig{howxy} (where the displaced test cases are found closer to  the training cases than the test cases) has been observed in all the other data sets studied in this
paper. Hence,  we can assert that
predictors learned from these training data have some authority in the regions
used to generate the plans\footnote{If the reader is concerned that this 2d projection
losses important information, then they should note that two separate  studies~\cite{papa13,divya15}
have confirmed that building defect predictors from this 2d space are just as effective
as predictors learned using all the defect attributes of \fig{ck}.}.
